Hierarchical Inference of the Intrinsic Ellipticity Distribution of Galaxies during Weak Lensing Analysis

### 2013-04-05 docs/ms.tex
Update ms.tex

In galaxy--galaxy lensing ,since the distortion is so weak,what people
usually do is stack many lensing signals together and get the mean
shear map,and then infers the mean mass profile of galaxy or galaxy
cluster. However with HB method we can avoid this brute averaging
, instead we can get the posterior distribution of mass profile for
each lensing system - even though it may have very large uncertainty- we
can calculate their statistical property like galaxy-mass correlation
function via this posterior distribution.

>>>>

In galaxy--galaxy lensing ,since the distortion is so weak,what people
usually do is stack many lensing signals together and get the mean
shear map,and then infers the mean mass profile of galaxy or galaxy
cluster. However with Hierarchical Bayesian method we can avoid this brute averaging
, instead we can get the posterior distribution of mass profile for
each lensing system - even though it may have very large uncertainty- we
can calculate their statistical property like galaxy-mass correlation
function via this posterior distribution.
